---
title             : "Lab 8 APA Manuscript Using Papaja in R"
shorttitle        : "Lab 8 Assignment"

author: 
  - name          : "Lisa Strycker"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Eugene, OR"
    email         : "lisas@ori.org"
  - name          : "Noah Strycker"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Oregon Research Institute"
  - id            : "2"
    institution   : "University of Oregon"
  - id            : "3"
    institution   : "Stony Brook University"
    
abstract: |
  Animal species have different behaviors for avoiding predators. Tonic immobility of a form of passive anti-predator behavior.
  
  In tonic immobility, organisms do not respond to external stimulation.
  
  Tonic immobility has been shown in isopods, including "sow bugs," but is largely unstudied. This study answered four research questions: (a) Do species differ in responsiveness to tonic immobility-inducing stimuli? (b) Does the responsiveness depend upon sex, size, or stimulus? (c) Is the duration of tonic immobility influenced by sex, size, or type of stimulus, and does it differ between species? (d) Is the duration of tonic immobility related to the time needed to elicit a response?
  
  Here we show that responses to external stimuli differ within and between three species of isopods. Three distinct patterns were found.
  
  Relatively stronger responses to different stimuli (e.g., drop, touch) may be because some species tend to have visual predators that are larger or smaller than they are. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "tonic immobility"

bibliography      : lab8_bibliography.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(janitor)
library(here)
library(rio)
library(knitr)
library(kableExtra)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE, error = FALSE, fig.width = 6.5, fig.height = 8.0)
```

```{r load data, echo = FALSE}
stardf <- import(here("data", "star.csv"))
stardf <- stardf %>%
  janitor::clean_names()
```

# Methods
Methods were similar to @quadros2012 and others [see @hoagland1927].

## Participants
Participants were sow bugs and students in public school.

## Material
Materials included forceps and teachers.

## Procedure
All procedures were approved by the Institutional Review Board. Sow bugs were debriefed after each trial. Children were informed that they could withdraw from the study at any time.

## Data analysis
Data were analyzed.

# Results

Results showed differences by gender and socioeconomic status in math and reading scores (see table). Results also indicated a positive relationship between years of teacher experience and total math scale score. The pattern was the same regardless of socioeconomic status, but students who paid for meals had higher math scale scores overall (see plot).

# Discussion
More studies are needed to investigative whether anti-predator strategies like tonic immobility improve survivorship. Future research should elucidate which responses work for different predators.
\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage 

```{r create_table, echo = FALSE}
stardf <- import(here("data", "star.csv"))
stardf <- stardf %>%
  janitor::clean_names()
stardf <- stardf %>%
  group_by(sex, frl) %>%
  summarize(math_mean = round(mean(tmathss), digits = 2), math_sd = round(sd(tmathss), digits = 2), rdg_mean = round(mean(treadss), digits = 2),  rdg_sd = round(sd(treadss), digits = 2))

stardf %>%
  kable(format = "latex") %>%
  kable_styling()
```

\newpage 

```{r create_graph, echo = FALSE}
stardf <- import(here("data", "star.csv"))

stardf <- stardf %>%
  janitor::clean_names()

ggplot(stardf, aes(x = totexp, y = tmathss)) + theme_minimal() + geom_point(color = "gray") + geom_smooth(aes(color = factor(frl, labels=c("Paid Meals", "Free/Reduced Price Meals"))), method = "lm", se = TRUE, size = 1) + labs(x = "Teacher Experience (years)", y = "Total Math Scale Score", color="Lunch status", title = "Relation between teacher experience and math scores", subtitle = "Separate regression  lines displayed by free/reduced price lunch status") + theme(legend.position="bottom")
```
